Report for Programming Assignment 1

### 2017-08-31 Programming-Assignment-1/PA-1_report.tex
PA-1 Update 10

From the above table it can be seen that for any setting of learning rate from the given values, the algorithm converges to the minimum for the convex functions: \(f_{Q}\) and \(f_{LL}\). This is natural from what we have learnt that gradient descent will eventually converge to the minimum for convex functions. In \(f_{H}\), convergence was seen for the step size being set to \(0.1\) and \(0.01\), but there was an oscillation observed in \(0.3\), hence the point got pushed away from the minimum. In the case of \(f_{R}\), the valley like structure makes the gradient updates slower and slower and hence none of the settings make it to the minimum.
\(\newline\)

The next Gradient Descent method used was Backtracking Line Search with Gradient Descent. Here we consider the approximation:
\begin{equation*}
f(\mathbf{x} + t\nabla f(\mathbf{x})) \approx f(\mathbf{x}) - t\alpha ||\nabla f(\mathbf{x})||^{2}_{2}
\end{equation*}

>>>>

From the above table it can be seen that for any setting of learning rate from the given values, the algorithm converges to the minimum for the convex functions: \(f_{Q}\) and \(f_{LL}\). This is natural from what we have learnt that gradient descent will eventually converge to the minimum for convex functions. In \(f_{H}\), convergence was seen for the step size being set to \(0.1\) and \(0.01\), but there was an oscillation observed in \(0.3\), hence the point got pushed away from the minimum.

\begin{figure}[H]
\begin{minipage}{0.32\linewidth}
\includegraphics[width=0.9\textwidth]{./images/himmelblau_0_01.eps}
\caption{\(f_{H}(x, y) \rightarrow \eta\) = 0.01}
\end{minipage}
\hfill
\begin{minipage}{0.32\linewidth}
\includegraphics[width=0.9\textwidth]{./images/himmelblau_0_1.eps}
\caption{\(f_{H}(x, y) \rightarrow \eta\) = 0.1}
\end{minipage}
\hfill
\begin{minipage}{0.32\linewidth}
\includegraphics[width=0.9\textwidth]{./images/himmelblau_0_3.eps}
\caption{\(f_{H}(x, y) \rightarrow \eta\) = 0.3}
\end{minipage}
\end{figure}
In the case of \(f_{R}\), the valley like structure makes the gradient updates slower and slower and hence none of the settings make it to the minimum.
\(\newline\)

The next Gradient Descent method used was Backtracking Line Search with Gradient Descent. Here we consider the approximation:
\begin{equation*}
f(\mathbf{x} + t\nabla f(\mathbf{x})) \approx f(\mathbf{x}) - t\alpha ||\nabla f(\mathbf{x})||^{2}_{2}
\end{equation*}
\(\newline\)
